An Empirical Analysis of the Role of Energy in Economic Growth

### 2013-07-13 EconGrowth.Rnw
Now using Randy's graph function for all SF scatter plots.

<<SFk_Resample_Graph, fig.pos="H", fig.width=ninePanelGraphWidth, fig.height=ninePanelGraphHeight, fig.cap="Single factor model (with $f = k$ and $m = \\alpha$) resampling results.", eval=TRUE>>=
standardScatterPlot(loadAllResampleData(model="sf", factor="K", 
                                        countryAbbrevsOrder=countryAbbrevsForGraph,
                                        countryAbbrevsOrderU=countryAbbrevsForGraphU), 
                    aes(m, lambda)) + 
  labs(x=expression(alpha), y=expression(lambda))
@

<<SFl_Resample_Graph, fig.pos="H", fig.width=ninePanelGraphWidth, fig.height=ninePanelGraphHeight, fig.cap="Single factor model (with $f = l$ and $m = \\beta$) resampling results.">>=
sfResamplePlot(factor="L")
@

<<SFq_Resample_Graph, fig.pos="H", fig.width=ninePanelGraphWidth, fig.height=ninePanelGraphHeight, fig.cap="Single factor model (with $f = q$ and $m = \\gamma$) resampling results.">>=
sfResamplePlot(factor="Q")
@

<<SFx_Resample_Graph, fig.pos="H", fig.width=ninePanelGraphWidth, fig.height=ninePanelGraphHeight, fig.cap="Single factor model (with $f = x$ and $m = \\gamma$) resampling results.">>=
sfResamplePlot(factor="X")
@

<<SFu_Resample_Graph, fig.pos="H", fig.width=ninePanelGraphWidth, fig.height=threePanelGraphHeight, fig.cap="Single factor model (with $f = u$ and $m = \\gamma$) resampling results.">>=
sfResamplePlot(factor="U")
@

>>>>

<<SFk_Resample_Graph, fig.pos="H", fig.width=ninePanelGraphWidth, fig.height=ninePanelGraphHeight, fig.cap="Single factor model (with $f = k$ and $m = \\alpha$) resampling results.", eval=TRUE>>=
standardScatterPlot(loadAllResampleData(model="sf", factor="K", 
                                        countryAbbrevsOrder=countryAbbrevsForGraph), 
                    aes(m, lambda)) + 
  labs(x=expression(alpha), y=expression(lambda))
@

<<SFl_Resample_Graph, fig.pos="H", fig.width=ninePanelGraphWidth, fig.height=ninePanelGraphHeight, fig.cap="Single factor model (with $f = l$ and $m = \\beta$) resampling results.", eval=TRUE>>=
standardScatterPlot(loadAllResampleData(model="sf", factor="L", 
                                        countryAbbrevsOrder=countryAbbrevsForGraph), 
                    aes(m, lambda)) + 
  labs(x=expression(beta), y=expression(lambda))
@

<<SFq_Resample_Graph, fig.pos="H", fig.width=ninePanelGraphWidth, fig.height=ninePanelGraphHeight, fig.cap="Single factor model (with $f = q$ and $m = \\gamma$) resampling results.", eval=TRUE>>=
standardScatterPlot(loadAllResampleData(model="sf", factor="Q", 
                                        countryAbbrevsOrder=countryAbbrevsForGraph), 
                    aes(m, lambda)) + 
  labs(x=expression(gamma), y=expression(lambda))
@

<<SFx_Resample_Graph, fig.pos="H", fig.width=ninePanelGraphWidth, fig.height=ninePanelGraphHeight, fig.cap="Single factor model (with $f = x$ and $m = \\gamma$) resampling results.", eval=TRUE>>=
standardScatterPlot(loadAllResampleData(model="sf", factor="X", 
                                        countryAbbrevsOrder=countryAbbrevsForGraph), 
                    aes(m, lambda)) + 
  labs(x=expression(gamma), y=expression(lambda))
@

<<SFu_Resample_Graph, fig.pos="H", fig.width=ninePanelGraphWidth, fig.height=threePanelGraphHeight, fig.cap="Single factor model (with $f = u$ and $m = \\gamma$) resampling results.", eval=TRUE>>=
standardScatterPlot(loadAllResampleData(model="sf", factor="U", 
                                        countryAbbrevsOrder=countryAbbrevsForGraphU), 
                    aes(m, lambda)) + 
  labs(x=expression(gamma), y=expression(lambda))
@
